Harmful Anti-Foreign Sentiments based on Concern for Competition Should be Recognized and Addressed

### 2023-02-19 outputs/paper/paper.qmd
edits

# Introduction

@@

Sociodemographics:

@@

# Ethical Implications

>>>>

=======
# Introduction

@@

Sociodemographics: \* Age Group \* Gender \* State \* German Citizen \* Marital Status \* Relationship status, single \* Religious Affiliation \* Education \* Occupation \* Income \* Household Size \* Subjective Social Status \* Male population: determining states with access to males by dividing the number of women by men aged 14 and 44 for each municipality \* Politics: left and right-leaning \* Politics: affiliated parties

Mate Competition: using a scale of agree or disagree \* Does the influx of male refugees make it difficult for non-immigrant german men to find female partners

Job Competition: using a scale of agree or disagree\
\* The inflow of young make refugees make it more difficult for young non-immigrant German men to find work/ jobs

Life Satisfaction: scale of 0-10 \* Satisfaction with life

Encountering Refugees \* How many KM is the closest refugee reception center from your home \* How many refugees do you believe have settled in your municipality in the last year \* In the last month, how many refugees have you encountered in the following locations

Attitudes Toward Refugees (national and local scale): using a scale of agree or disagree \* Violence is sometimes the only means that citizens have to get the attention of German politicians \* Attitudes towards Muslims \* Hostility against refugees justified \* Politicians should condemn attacks against refugees \* Racist violence is defensible if it leads to fewer refugees settling in a town \* Attacks against refugee homes are sometimes necessary to make garner the attention of politicians \* Refugee integration in Germany \* German refugees should be entitled to German citizenship \* The number of refugees should be reduced \* Refugees are receiving more than non-immigrant Germans \* Refugees should give up their culture to adopt that of Germany \* Refugees are good for the economy \* Refugees increase crime \* Increased refugees increase the risk of terrorism \* Will additional refugees in your town increase the influence of Islam (local) \* Will additional refugees in your town be a challenge for local schools (local) \* Will additional refugees in your town increase competition for housing (local) \* Will additional refugees in your town change the way of life in your town (local)

Operational category \* Experiement lists \* Treatement lists \* Outcome lists \* Waves: out of 4

# \## Ethical Implications

=======
Sociodemographics:

@@
